Online learning apps from the learning cycle perspective: recent advances and best practices

### 2023-05-02 paper.Rmd
Update paper.rmd

---
title: "Online learning apps from the learning cycle perspective: recent advances and best practices"
author: Maria Osipenko^[Hochschule für Wirtschaft und Recht Berlin; osipenko@hwr-berlin.de] and Mara Lein ^[Hochschule für Wirtschaft und Recht Berlin]
date: ""
output: 
 bookdown::html_document2:
    fig_caption: yes
bibliography: [references.bib] 
link-citations: yes
linkcolor: blue
---

@@

```{r, echo=F}
##https://github.com/ropensci/openalexR
#remotes::install_github("ropensci/openalexR")
#options(openalexR.mailto = "mariaosipenko@yahoo.de")

#for pdf (does not compile because of unicode character checkmark U+2713)
 # bookdown::pdf_document2:
 #    toc: false
 #    fig_caption: yes
 #    keep_tex: true
```

```{r,echo=F}
# https://bookdown.org/joone/ComputationalMethods/topicmodeling.html
# library(tidyverse)
# library(tidytext)
# library(stm)
```

@@

```{r, echo=F, include=F}
#set up document-term matrix using the titles and the abstracts of the search result.

#install.packages("quanteda")
library(quanteda)
```

@@

for (i in 1:length(keyword_texts$name)){
  keyword_texts[i,2]<-as.character(paste(readLines(paste0("5E/",keyword_texts$name[[i]],".txt")),collapse=" "))
}
mydfm2<-make_dfm(keyword_texts$description)
keywords<-list()

for(i in 1:nrow(keyword_texts)){
  keywords[[i]]<-names(topfeatures(mydfm2[i,],100))
}

@@

```{r, echo=F, include=F}
names(keywords)<-keyword_texts$name

@@

TODO:
- review 25 articles per topic
- add references to R packages
- add references to the articles reviewed

>>>>

---
title: "Online learning apps from the learning cycle perspective: recent advances and best practices"
author: Maria Osipenko^[Hochschule für Wirtschaft und Recht Berlin; osipenko@hwr-berlin.de] and Mara Lein ^[Hochschule für Wirtschaft und Recht Berlin]
date: ""
output:
  md_document:
    variant: markdown_github
bibliography: [references.bib] 
link-citations: yes
linkcolor: blue
---

@@

@@

```{r, echo=F, include=F}
#set up document-term matrix using the titles and the abstracts of the search result.
#install.packages("quanteda")
library(quanteda)
```

@@

@@

```{r, echo=F, include=F}
keywords<-as.list(1:6)
names(keywords)<-keyword_texts$name

@@

[Try it yourself!] (https://rshiny.f4.htw-berlin.de/topics_keywords_app/)

### 2023-05-02 review_learning_dashboards_paper/paper.Rmd
Update paper.rmd

#for pdf (does not compile because of unicode character checkmark U+2713)
 # bookdown::pdf_document2:
 #    toc: false
 #    fig_caption: yes
 #    keep_tex: true
```

@@

## Explore your own keywords and their relation to topics

@@

TODO:
- review 25 articles per topic
- add references to R packages
- add references to the articles reviewed

>>>>

#for pdf (does not compile because of unicode character checkmark U+2713)
 # bookdown::pdf_document2:
 #    toc: false
 #    fig_caption: yes
 #    keep_tex: true

@@

## Explore your own keywords and their relation to topics{-}

@@

<iframe src="https://rshiny.f4.htw-berlin.de/topics_keywords_app/" height="800" width="1000" style="border: 1px solid #464646;" allowfullscreen="" allow="autoplay" data-external="1"></iframe>

TODO:

- review 25 articles per topic
- add references to R packages
- add references to the articles reviewed
